NumPy---Array Computation for Python

### 2020-01-08 body.tex
Fix typos

NumPy was initially developed by students, faculty, and researchers in their
spare time to provide a modern array computation library for Python.
They were influenced by their experiences with powerful interactive programming
languages for scientific computing like Yurik \cite{munro1995using} as well
as commercial languages like IDL and Matlab.
Often they developed code to solve their own or their colleagues problems.

As Python's popularity for scientific computing, data science, and machine
learning increased, many new use cases arose.
At the same time, the massive number of scientific Python packages that
build on NumPy mean that it has an unusually high need for stability.

>>>>

NumPy was initially developed by students, faculty, and researchers in their
spare time to provide a modern array computation library for Python.
They were influenced by their experiences with powerful interactive programming
languages for scientific computing like Yorick \cite{munro1995using} as well
as commercial languages like IDL and Matlab.
Often they developed code to solve their own or their colleagues' problems.

As Python's popularity for scientific computing, data science, and machine
learning increased, many new use cases arose.
At the same time, the massive number of scientific Python packages that
built on NumPy meant that it had an unusually high need for stability.
